Reproduction

### 2024-10-17 pages/relationship_reproduction_evaluation.qmd
chore(docs): add TODO to several pages

>>>>

TODO: I'm also interested actually particularly in relationship between "reflections" being met, and reproduction.

*this could be more restructured into (a) reflections from evaluations, similar to as I have for reproductions, then supported by the side by side evidence, and then (b) adding that side by side evidence to the existing reflections from reproductions*

TODO: For reflections on evaluations, add reflection that a lack of provision of ORCID or citation information didn't have a big impact here, as I was choosing repositories that I had found from papers, so I already at least knew who the paper authors were. Although that doesn't mean that any attempted citation of the repository itself would've necessarily been correct, depending on whether the author list would be the same.

*add some scatter plots to repo evaluation but not sure how helpful they are*

### 2024-10-17 pages/reproduction.qmd
chore(docs): add TODO to several pages

>>>>

::: {.callout icon=false collapse=false}

## Reproduction reflections

**TODO: Where possible, reflect on what I think to be the primary reason that didn't manage to fully reproduce despite troubleshooting, for the studies where this was the case**

:::

::: {.callout icon=false collapse=false}

## Timing reflections

**TODO: Reflect on these timings - what I think were the primary reason for things to be quicker or slower - and what I think was relevant/important** <!--e.g. models with run long times, experimenting with parameters to run it quicker, in order to more easily troubleshoot, else run for long time then discover xyz is wrong-->

:::
